---
title: "09_Cohorts_survival"
author: "Balazs Koncz"
date: '2020 12 04 '
output: html_document
---

#Setup

```{r}
setwd("d:/CloudStation/mygit/TCEM_related_vars/IT_cohorts/")
ext_folder1 = "d:/CloudStation/mygit_EXT/TCEM_related_vars/IT_cohorts/"
packs <- c("magrittr", "tibble", "fastmatch", "ggplot2", "stringr", "forcats", "stringi", "Rfast", "tidyr", "parallel", "survival", "survminer", "testit", "beepr", "ComplexHeatmap", "circlize", "gridExtra", "pbapply", "readxl", "ggpubr", "Hmisc")
invisible(lapply(packs, require, character.only = TRUE))
rm(packs)
```

#Patients characteristics

```{r}
chowell_data = read_excel(paste0(ext_folder1, "objects/aao4572_Chowell_SM-Table-S9.xlsx"))
ids = list.files(paste0(ext_folder1, "08out/tcem_mutated_nonamers/"))

snyder = 

mutcnt = pbsapply(ids, function(x) {
  load(paste0(ext_folder1, "08out/tcem_mutated_nonamers/", x))
  length(unique(nonamers$mut))
})

load(paste0(ext_folder1, "objects/c1c2"))
c1c2 = c1c2[,c("Sample", "OS_Months", "OS_Event", "Drug.Class", "Cancer.Type")]
colnames(c1c2)[1] = "sampleid"

vallen = read_excel(paste0(ext_folder1, "objects/TableS2_Revised.xlsx"))
vallen = vallen[,c("patient", "age_start", "overall_survival", "dead")]
colnames(vallen)[c(1,4)] = c("sampleid","OS_Event")
vallen$OS_Months = vallen$overall_survival/30.417
vallen$Drug.Class = "CTLA-4"
vallen$Cancer.Type = "Melanoma"
# vallen$Age.Group = NA
# vallen$Age.Group[vallen$age_start < 30] = "<30"
# vallen$Age.Group[vallen$age_start > 30 & vallen$age_start <= 50] = "31-50"
# vallen$Age.Group[vallen$age_start > 50 & vallen$age_start <= 60] = "50-60"
# vallen$Age.Group[vallen$age_start > 60 & vallen$age_start <= 70] = "61-70"
# vallen$Age.Group[vallen$age_start > 70] = ">71"
# vallen$Age.Group = factor(vallen$Age.Group, levels = c("<30","31-50","50-60","61-70",">71"))

vallen = vallen[,c("sampleid", "OS_Months", "OS_Event", "Drug.Class", "Cancer.Type")]


c1c2 = c1c2[!c1c2$sampleid %in% vallen$sampleid,]
vallen = vallen[vallen$sampleid %in% ids,]
c1c2 = c1c2[c1c2$sampleid %in% ids,]
#unique(dtann$sampleid[!dtann$sampleid %in% c1c2$Sample])
pat_char = rbind(c1c2, vallen)
pat_char = cbind(pat_char, TMB = mutcnt[match(pat_char$sampleid, names(mutcnt))])

save(pat_char, file = paste0(ext_folder1, "09out/pat_char"))
```

#Analysis 1
TP score is very good predictor!

##Calculate ratios
Ratio of neononamers with low TCEM frequency (<4), low TCEM expression and low TCEM thymoproteasomal score
cutoff: 33% - 0.203075, 66% - 1.095007
cutoff: 25%: 0.914470

```{r}
load(paste0(ext_folder1, "objects/pentamerfreq_tcem"))
load(paste0(ext_folder1, "objects/exprmeds"))
load(paste0(ext_folder1, "objects/thymomeds"))
# load("D:/CloudStation/pentamer_project/objects/score_list_ipr_normalized_with_division_median_two_sides")
# immunomeds = pbsapply(score_list, function(x) median(x))
# rm(score_list)
# save(immunomeds, file = paste0(ext_folder1, "objects/immunomeds"))
load(paste0(ext_folder1, "objects/immunomeds"))
cutp_expr1 = 0.203075
cutp_expr2 = 1.095007
cutp_th = 0.914470
cutp_im1 = median(immunomeds, na.rm = T)
cutp_im2 = unname(quantile(immunomeds,.75,na.rm = T))
cutp_im3 = unname(quantile(immunomeds,.9,na.rm = T))

ids = list.files(paste0(ext_folder1, "08out/tcem_mutated_nonamers/"))
vals = c("neoaffweak", "neoaffstr", "neorpweak", "neorpstr")


sort(pbsapply(ids, function(x) {
  load(paste0(ext_folder1, "08out/tcem_mutated_nonamers/", x))
  nrow(nonamers)
}))

i=0
pat_ratio = t(pbsapply(ids, function(x) {
  i = i+1
  .GlobalEnv$i = i
  
  load(paste0(ext_folder1, "08out/tcem_mutated_nonamers/", x))
  
  ratios = lapply(vals, function(y) {
    tdf = nonamers %>% dplyr::rename(binding = y) %>% dplyr::filter(binding == TRUE)
    #FREQ
    nf = nrow(tdf)
    lf = sum(tdf$neofreq<4)/nf
    lorhf = sum(tdf$neofreq<4 | tdf$neofreq>=8) / nf
    #EXPR
    tdf_expr = subset(tdf, !is.na(neoexpr))
    ne = nrow(tdf_expr)
    le = sum(tdf_expr$neoexpr<cutp_expr1) / ne
    lorhe = sum(tdf_expr$neoexpr<cutp_expr1 | tdf_expr$neoexpr>cutp_expr2) / ne
    #THYMO
    tdf_thymo = subset(tdf, !is.na(neothymo))
    nt = nrow(tdf_thymo)
    lt = sum(tdf_thymo$neothymo<cutp_th) / nt
    
    #combinations - 2
    ##FREQ & EXPR
    lfle = sum(tdf_expr$neofreq<4 & tdf_expr$neoexpr<cutp_expr1) / ne
    lorhfle = sum((tdf_expr$neofreq<4 | tdf_expr$neofreq>=8) & tdf_expr$neoexpr<cutp_expr1) / ne
    lflorhe = sum(tdf_expr$neofreq<4 & (tdf_expr$neoexpr<cutp_expr1|tdf_expr$neoexpr>=cutp_expr2)) / ne
    lorhflorhe = sum((tdf_expr$neofreq<4 | tdf_expr$neofreq>=8) & (tdf_expr$neoexpr<cutp_expr1|tdf_expr$neoexpr>=cutp_expr2)) / ne
    ##FREQ & THYMO
    lflt = sum(tdf_thymo$neofreq<4 & tdf_thymo$neothymo<cutp_th) / nt
    lorhflt = sum((tdf_thymo$neofreq<4 | tdf_thymo$neofreq>=8) & tdf_thymo$neothymo<cutp_th) / nt
    ##EXPR & THYMO
    tdf_et = subset(tdf, !is.na(neoexpr) & !is.na(neothymo))
    net = nrow(tdf_et)
    lelt = sum(tdf_et$neoexpr<cutp_expr1 & tdf_et$neothymo<cutp_th) / net
    lorhelt = sum((tdf_et$neoexpr<cutp_expr1|tdf_et$neoexpr>=cutp_expr2) & tdf_et$neothymo<cutp_th) / net
    
    #combination - 3
    lflelt = sum(tdf_et$neofreq<4 & tdf_et$neoexpr<cutp_expr1 & tdf_et$neothymo<cutp_th) / net
    lorhflelt = sum((tdf_et$neofreq<4 | tdf_et$neofreq>=8) & tdf_et$neoexpr<cutp_expr1 & tdf_et$neothymo<cutp_th) / net
    lflorhelt = sum(tdf_et$neofreq<4 & (tdf_et$neoexpr<cutp_expr1 | tdf_et$neoexpr>=cutp_expr2) & tdf_et$neothymo<cutp_th) / net
    lorhflorhelt = sum((tdf_et$neofreq<4 | tdf_et$neofreq>=8) & (tdf_et$neoexpr<cutp_expr1 | tdf_et$neoexpr>=cutp_expr2) & tdf_et$neothymo<cutp_th) / net
    
    #immuno - higher than cutoffs
    tdf_immuno = subset(tdf, !is.na(neoimmuno))
    ni = nrow(tdf_immuno)
    hi1 = sum(tdf_immuno$neoimmuno>cutp_im1) / ni
    hi2 = sum(tdf_immuno$neoimmuno>cutp_im2) / ni
    hi3 = sum(tdf_immuno$neoimmuno>cutp_im3) / ni
    ratios = c(nf, ne, nt, net, ni, lf, lorhf, le, lorhe, lt, lfle, lorhfle, lflorhe, lorhflorhe, lflt, lorhflt, lelt, lorhelt, lflelt, lorhflelt, lflorhelt, lorhflorhelt, hi1, hi2, hi3) #vars*
    ratios
  })
  ratios = do.call(rbind, ratios)
  colnames(ratios) = c("nFREQ", "nEXPR", "nTHYMO", "nEXPR_THYMO", "nIMMUNO", "FREQ_low", "FREQ_loh", "EXPR_low", "EXPR_loh", "THYMO_low", "FREQ_low_EXPR_low", "FREQ_loh_EXPR_low", "FREQ_low_EXPR_loh", "FREQ_loh_EXPR_loh", "FREQ_low_THYMO_low", "FREQ_loh_THYMO_low", "EXPR_low_THYMO_low", "EXPR_loh_THYMO_low", "FREQ_low_EXPR_low_THYMO_low", "FREQ_loh_EXPR_low_THYMO_low", "FREQ_low_EXPR_loh_THYMO_low", "FREQ_loh_EXPR_loh_THYMO_low", "hi1", "hi2", "hi3")
  ratios = as.data.frame(ratios)
  ratios = cbind(binding = vals, ratios)
  ratios = pivot_wider(data = ratios, names_from = binding, values_from = 2:26, names_glue = "{binding}_{.value}")
  cn = colnames(ratios)
  ratios = as.numeric(ratios)
  names(ratios) = cn
  ratios
}))

pat_ratio = as.data.frame(pat_ratio)
save(pat_ratio, file = paste0(ext_folder1,"09out/pat_ratio"))

load(paste0(ext_folder1, "09out/pat_char"))
cohort = cbind(pat_char, pat_ratio[match(pat_char$sampleid, rownames(pat_ratio)),])
save(cohort, file = paste0(ext_folder1, "09out/cohort"))
```

##Survival

```{r}
load(paste0(ext_folder1,"09out/cohort"))
tcemvars = grep("_l|_h", colnames(cohort), value = T)
res = expand.grid(tumor = c("all", unique(cohort$Cancer.Type)), tcemv = tcemvars, tcemv.cutpoint = seq(0.05,0.6,0.05), tcemv_filter = c("no", "yes"), stringsAsFactors = F)
res_ftest = res
res %<>%
  mutate(m34n = NA, TMBcor_rho = NA, TMBcor_p = NA, m3coef = NA, m3p = NA, m3warning = NA,
         m4lown = NA, m4highn = NA, m4coef = NA, m4p = NA, m4warning = NA)
res_ftest %<>%
  mutate(m3p = NA, m3globalp = NA, m3warning = NA, m4p = NA, m4globalp = NA, m4warning = NA)


for(i in 1:nrow(res)) {
  tryCatch({  
    print(i)
    temptcemvar = res$tcemv[i]
    tempcountvar = value_count_var_matching$countvar[value_count_var_matching$tcemvar == temptcemvar]
    cohort_f = cohort %>% 
      dplyr::rename(countvar = tempcountvar, tcemvar = temptcemvar) %>% 
      dplyr::filter(!is.na(tcemvar))
    #Select tumor
    if(res$tumor[i] != "all") cohort_f %<>% dplyr::filter(Cancer.Type == res$tumor[i])
    if(nrow(cohort_f) < 20) next()
    #select tcemvars
    cohort_f %<>% 
      dplyr::select(sampleid, Age.Group, , countvar, tcemvar, OS_Event, OS_Months)
    #filter neopep count connected to tcemvar
    if(res$tcemv_filter[i] == "yes") cohort_f %<>% dplyr::filter(countvar >= 10) #legalabb 10 neopeptid legyen
    if(nrow(cohort_f) < 20) next()
    #Create TCEM freq group
    cohort_f$tcemvargroup = cut(x = cohort_f$tcemvar, breaks = c(0,res$tcemv.cutpoint[i],1), include.lowest = T, labels = F, right = F)
    cohort_f %<>% na.omit()
    if(nrow(subset(cohort_f, OS_Event == 1)) <= 3) next()
    res$m34n[i] = nrow(cohort_f)
    res$TMBcor_rho[i] = cor.test(cohort_f$TMB, cohort_f$tcemvar, method = "spearman")$estimate
    res$TMBcor_p[i] = cor.test(cohort_f$TMB, cohort_f$tcemvar, method = "spearman")$p.value
    if(nrow(cohort_f) < 20) next()
    m3 = coxph(Surv(OS_Months, OS_Event) ~ Age.Group + TMB + tcemvar, data = cohort_f)
    res$m3coef[i] = as.matrix(coef(summary(m3)))["tcemvar","coef"]
    res$m3p[i] = as.matrix(coef(summary(m3)))["tcemvar","Pr(>|z|)"]
    res$m3warning[i] = has_warning(coxph(Surv(OS_Months, OS_Event) ~ Age.Group + TMB + tcemvar, data = cohort_f))
    ftestm3 = cox.zph(m3)
    res_ftest$m3p[i] = ftestm3$table["tcemvar","p"]
    res_ftest$m3globalp[i] = ftestm3$table["GLOBAL","p"]
    res_ftest$m3warning[i] = has_warning(cox.zph(coxph(Surv(OS_Months, OS_Event) ~ Age.Group + TMB + tcemvar, data = cohort_f)))
    res$m4lown[i] = table(cohort_f$tcemvargroup)["1"]
    res$m4highn[i] = table(cohort_f$tcemvargroup)["2"]
    if(length(unique(cohort_f$tcemvargroup)) < 2) next()
    m4 = coxph(Surv(OS_Months, OS_Event) ~ Age.Group + TMB + tcemvargroup, data = cohort_f)
    res$m4coef[i] = as.matrix(coef(summary(m4)))["tcemvargroup","coef"]
    res$m4p[i] = as.matrix(coef(summary(m4)))["tcemvargroup","Pr(>|z|)"]
    res$m4warning[i] = has_warning(coxph(Surv(OS_Months, OS_Event) ~ Age.Group + TMB + tcemvargroup, data = cohort_f))
    ftestm4 = cox.zph(m4)
    res_ftest$m4p[i] = ftestm4$table["tcemvargroup","p"]
    res_ftest$m4globalp[i] = ftestm4$table["GLOBAL","p"]
    res_ftest$m4warning[i] = has_warning(cox.zph(coxph(Surv(OS_Months, OS_Event) ~ Age.Group + TMB + tcemvargroup, data = cohort_f)))
  }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}

rm(cohort_f, ftestm3, ftestm4, m3, m4, i, tempcountvar, temptcemvar)

colnames(res_ftest)[5:10] = paste("ftest", colnames(res_ftest)[5:10], sep = "_")
res = cbind(res, res_ftest[,5:10])
rm(res_ftest)
save(res, file = paste0(ext_folder1,"09out/survival"))
beep(sound = "ping")


```

##Results:

```{r}
load(paste0(ext_folder1,"09out/survival"))
res %>% 
  dplyr::filter(tcemv_filter == "yes", m3p < 0.05, m4p < 0.05) %>% 
  View()
res %>% 
  dplyr::filter(tcemv_filter == "yes", m3p < 0.05, m4p < 0.05, m4lown >= 20, m4highn >= 20) %>% 
  View()

res %>% 
  dplyr::filter(tcemv_filter == "yes", m3p < 0.05, m4p < 0.05) %>% 
  dplyr::select(tcemv) %>% 
  table() %>% 
  sort()

res %>% 
  dplyr::filter(tcemv_filter == "yes", m3p < 0.05, m4p < 0.05, m4lown >= 20, m4highn >= 20) %>% 
  dplyr::select(tcemv) %>% 
  table() %>% 
  sort()



```

##EXPR_loh_THYMO_low
EXPR,THYMO:
neoaffstr_EXPR_loh_THYMO_low ALL:3508,SKCM:3509
neoaffweak_EXPR_loh_THYMO_low ALL:3745 (ns), SKCM:3746
neorpstr_EXPR_loh_THYMO_low ALL:3754 (ns), SKCM:3755
neorpweak_EXPR_loh_THYMO_low ALL:3511 (ns), SKCM:3512 - leggyengebb

```{r}
res %>% 
  dplyr::filter(tcemv %in% c("neoaffstr_EXPR_loh_THYMO_low","neoaffweak_EXPR_loh_THYMO_low","neorpstr_EXPR_loh_THYMO_low","neorpweak_EXPR_loh_THYMO_low"), m4lown >= 10, m4highn >= 10) %>% 
  View()

View(res[c(3508,3509,3745,3746,3754,3755,3511,3512),])
```

##THYMO_low:
neoaffstr_THYMO_low ALL:4132, SKCM:4133 (ns)
neoaffweak_THYMO_low ALL:4129,SKCM:4130
neorpstr_THYMO_low ALL:4138 (ns), SKCM:4139 (ns)
neorpweak_THYMO_low ALL:4135 (ns),SKCM:4136 (ns)

```{r}
res %>% 
  dplyr::filter(tcemv %in% c("neoaffstr_THYMO_low","neoaffweak_THYMO_low","neorpstr_THYMO_low","neorpweak_THYMO_low"), m4lown >= 10, m4highn >= 10) %>% 
  View()
View(res[c(4132,4133,4129,4130,4138,4139,4135,4136),])
```

##FREQ_low_THYMO_low
neoaffstr_FREQ_low_THYMO_low ALL:3232,SKCM:3233
neoaffweak_FREQ_low_THYMO_low - ns
neorpstr_FREQ_low_THYMO_low - ns
neorpweak_FREQ_low_THYMO_low - ns

##FREQ_loh_THYMO_low
neoaffstr_FREQ_loh_THYMO_low ALL: 3964 SKCM: 3965
neoaffweak_FREQ_loh_THYMO_low ALL:3961 SKCM:3962
neorpstr_FREQ_loh_THYMO_low ns
neorpweak_FREQ_loh_THYMO_low ns

##FREQ_loh_EXPR_loh_THYMO_low
neoaffstr_FREQ_loh_EXPR_loh_THYMO_low ALL:3556, SKCM:3557 - kiegyenlitetlen
neoaffweak_FREQ_loh_EXPR_loh_THYMO_low ALL:3553, SKCM:3554 - kiegyenlitetlen
neorpstr_FREQ_loh_EXPR_loh_THYMO_low ALL:3562(ns), SKCM:3563 - kiegyenlitetlen
neorpweak_FREQ_loh_EXPR_loh_THYMO_low ns


##Plot

```{r}
load(paste0(ext_folder1,"09out/survival"))
load(paste0(ext_folder1,"09out/cohort"))
load(paste0(ext_folder1,"09out/value_count_var_matching"))

i = 4136
temptcemvar = res$tcemv[i]
tempcountvar = value_count_var_matching$countvar[value_count_var_matching$tcemvar == temptcemvar]
cohort_f = cohort %>% 
  dplyr::rename(countvar = tempcountvar, tcemvar = temptcemvar) %>% 
  dplyr::filter(!is.na(tcemvar))
if(res$tumor[i] != "all") cohort_f %<>% dplyr::filter(Cancer.Type == res$tumor[i])
cohort_f %<>% 
  dplyr::select(sampleid, Age.Group, TMB, countvar, tcemvar, OS_Event, OS_Months)
if(res$tcemv_filter[i] == "yes") cohort_f %<>% dplyr::filter(countvar >= 10) #legalabb 10 neopeptid legyen
cohort_f$tcemvargroup = cut(x = cohort_f$tcemvar, breaks = c(0,res$tcemv.cutpoint[i],1), include.lowest = T, labels = F, right = F)
cohort_f %<>% na.omit()
nrow(cohort_f)
cor.test(cohort_f$TMB, cohort_f$tcemvar, method = "spearman")
ggplot(cohort_f, aes(TMB, tcemvar)) + geom_point() + geom_smooth() + stat_cor(method = "spearman")
ggsave(file = paste0(ext_folder1,"09out/plots/", paste0(as.character(res[i,1:4]), collapse = "_"), "cor.jpg"), width = 20, height = 20, units = "cm", dpi = "retina")

coxph(Surv(OS_Months, OS_Event) ~ Age.Group + TMB + tcemvar, data = cohort_f)
has_warning(coxph(Surv(OS_Months, OS_Event) ~ Age.Group + TMB + tcemvar, data = cohort_f))
cox.zph(coxph(Surv(OS_Months, OS_Event) ~ Age.Group + TMB + tcemvar, data = cohort_f))
coxph(Surv(OS_Months, OS_Event) ~ Age.Group + TMB + tcemvargroup, data = cohort_f)
table(cohort_f$tcemvargroup)
has_warning(coxph(Surv(OS_Months, OS_Event) ~ Age.Group + TMB + tcemvargroup, data = cohort_f))
cox.zph(coxph(Surv(OS_Months, OS_Event) ~ Age.Group + TMB + tcemvargroup, data = cohort_f))
has_warning(cox.zph(coxph(Surv(OS_Months, OS_Event) ~ Age.Group + TMB + tcemvargroup, data = cohort_f)))

survp = ggsurvplot(fit = survfit(Surv(time = OS_Months, event = OS_Event) ~ tcemvargroup, data = cohort_f), pval = TRUE, legend.title = res$tcemv[i], surv.median.line = c("hv"), title = paste(c("Dataset:", res[i,1:4]), sep = " ", collapse = " "), font.main = 8, risk.table = T)
pdf(paste0(ext_folder1,"09out/plots/", paste0(as.character(res[i,1:4]), collapse = "_"), "survival_plot.pdf"))
print(survp, newpage = FALSE)
dev.off()


ggforest(coxph(Surv(OS_Months, OS_Event) ~ Age.Group + TMB + tcemvar, data = cohort_f), data = cohort_f)
ggsave(file = paste0(ext_folder1,"09out/plots/", paste0(as.character(res[i,1:4]), collapse = "_"), "ggforest.jpg"), width = 20, height = 20, units = "cm", dpi = "retina")
ggforest(coxph(Surv(OS_Months, OS_Event) ~ Age.Group + TMB + tcemvargroup, data = cohort_f), data = cohort_f)
ggsave(file = paste0(ext_folder1,"09out/plots/",paste0(as.character(res[i,1:4]), collapse = "_"), "ggforest_cont.jpg"), width = 20, height = 20, units = "cm", dpi = "retina")

rm(cohort_f, survp, i, tempcountvar, temptcemvar)
```

##Correlation with mutation

```{r}
load(paste0(ext_folder1,"09out/survival"))
load(paste0(ext_folder1,"09out/cohort"))

tcemvars = grep("_l|_h", colnames(cohort), value = T)

cormat <- cbind(rho = sapply(tcemvars, function(x) cor.test(cohort$TMB, cohort[,x], method = "spearman")$estimate), p.value = sapply(tcemvars, function(x) cor.test(cohort$TMB, cohort[,x], method = "spearman")$p.value))
cormat = as.data.frame(cormat)
cormat = cbind.data.frame(tcemvars, cormat)
rownames(cormat) = NULL
save(cormat, file = paste0(ext_folder1,"09out/correlation"))

cohort_f = subset(cohort, affweak_lt > 0)
Hmisc::rcorr(x = cohort_f$TMB, y = cohort_f$affweak_lt, type = "spearman")
ggplot(cohort, aes(TMB, affweak_lt)) + geom_point() + scale_x_continuous(trans = "log2") + geom_smooth() + stat_cor(method = "spearman")
ggplot(cohort, aes(TMB, affweak_lt)) + geom_point() + geom_smooth() + stat_cor(method = "spearman")
```



##Low mutation count and high ratio of epitopes with low thymoproteasome score

```{r}
load(paste0(ext_folder1,"09out/survival"))
load(paste0(ext_folder1,"09out/cohort"))

cohort_f = cohort %>% 
  dplyr::filter(!is.na(affweak_lt)) %>% 
  dplyr::filter(affweak_nt >= 10) %>% 
  dplyr::select(sampleid, TMB, affweak_lt, OS_Months, OS_Event) 

cohort_f$TMB_group = cut(x = cohort_f$TMB, breaks = c(0,median(cohort_f$TMB),Inf), include.lowest = T, labels = F, right = F)
table(cohort_f$TMB_group)

cohort_f$affweak_lt_group = cut(x = cohort_f$affweak_lt, breaks = c(0,.3,1), include.lowest = T, labels = F, right = T)
table(cohort_f$affweak_lt_group)

cohort_f$group = NA
cohort_f$group[cohort_f$TMB < median(cohort_f$TMB) & cohort_f$affweak_lt > .3] = 1
cohort_f$group[cohort_f$TMB > median(cohort_f$TMB) & cohort_f$affweak_lt < .3] = 2 #ennek varjuk a jobb tuleleset
table(cohort_f$group)

ggsurvplot(fit = survfit(Surv(time = OS_Months, event = OS_Event) ~ TMB_group, data = cohort_f), pval = TRUE, surv.median.line = c("hv"), font.main = 8, risk.table = T)
ggsurvplot(fit = survfit(Surv(time = OS_Months, event = OS_Event) ~ affweak_lt_group, data = cohort_f), pval = TRUE, surv.median.line = c("hv"), font.main = 8, risk.table = T)
ggsurvplot(fit = survfit(Surv(time = OS_Months, event = OS_Event) ~ group, data = cohort_f), pval = TRUE, surv.median.line = c("hv"), font.main = 8, risk.table = T)

```

